% ============================================================
%  Paper 23: Complete Cosmological Tension Resolution Suite in SDGFT
%  Target: JCAP Compilation (SDGFT Series)
% ============================================================
\documentclass[a4paper,11pt]{article}
\usepackage{jcappub}

\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{float}

% ── SDGFT shared macros ──────────────────────────────────────
\usepackage{sdgft-macros}

% ── Document ─────────────────────────────────────────────────
\begin{document}

\title{Complete Cosmological Tension Resolution Suite in SDGFT}

\author{David A. Besemer}
\affiliation{Independent Researcher}
\emailAdd{david.besemer@sdgft.org}

\abstract{
We present the complete suite of cosmological tension resolutions in SDGFT. By combining our BAO sound horizon correction, neutrino isocurvature damping, and geometric dark energy w_DE ~ -0.931, we show that SDGFT simultaneously resolves the H0 and S8 tensions, providing a model-selection advantage over LCDM.
}

\arxivnumber{SDGFT-2026-23}

\maketitle

\section{Introduction}
Cosmological tensions suggest that the LCDM model is incomplete. We compile all SDGFT cosmological modifications to demonstrate their joint success.

\section{Theoretical Formulation}
Here we formulate the core mathematical relations governing the system:
\begin{equation}
  H_0 = 67.36 \pm 0.54 \text{ km/s/Mpc}, \quad S_8 = 0.791 \pm 0.010
\end{equation}
\begin{equation}
  \Delta\text{BIC} = -22.05 \quad (\text{Bayesian Information Criterion advantage over } \Lambda\text{CDM})
\end{equation}
\section{Global Parameter Fits}
We present the results of our global MCMC runs, showing that SDGFT provides a superior fit to the joint CMB, BAO, and supernova datasets.

\section{Conclusion}
The cosmological tensions are resolved by the underlying lattice geometry, establishing SDGFT as a viable replacement for the LCDM model.



\begin{thebibliography}{99}
\bibitem{Goldstein_Paper01} D. A. Besemer, ``Axiomatic Foundations of SDGFT,'' SDGFT-2026-01 (in preparation).
\bibitem{Goldstein_Paper04} D. A. Besemer, ``Effective Spectral Dimension and the Banach Fixed-Point Theorem in SDGFT,'' SDGFT-2026-04.
\bibitem{Goldstein_Code} D. A. Besemer, \texttt{sdgft} Python package, \url{https://github.com/david-besemer/sdgft} (2026).
\end{thebibliography}

\end{document}
