% ============================================================
%  Paper 04: Effective Spectral Dimension and the Banach Fixed-Point Theorem in SDGFT
%  Target: RevTeX 4-2 Compilation (SDGFT Series)
% ============================================================
\documentclass[amsmath,amssymb,aps,prd,twocolumn,superscriptaddress,nofootinbib]{revtex4-2}

\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{float}
\usepackage{amsthm}
\newtheorem{theorem}{Theorem}

% ── SDGFT shared macros ──────────────────────────────────────
\usepackage{sdgft-macros}

% ── Document ─────────────────────────────────────────────────
\begin{document}

\preprint{SDGFT-2026-04}

\title{Effective Spectral Dimension and the Banach Fixed-Point Theorem in SDGFT}

\author{David A. Besemer}
\email{david.besemer@sdgft.org}
\affiliation{Independent Researcher}

\date{\today}

\begin{abstract}
We prove the existence and uniqueness of the effective spectral dimension D* in SDGFT. By formulating the continuous flow operator T(D) = Delta^(-1/D) * phi * Delta^(Delta * delta), we prove that it satisfies the Banach contraction theorem on the interval [2.4, 3.6]. The analytical derivative yields a Lipschitz bound of |T'(D)| < 0.836, driving the Picard iteration to converge to D* ~ 2.79676 in exactly 60 steps to machine precision.
\end{abstract}

\maketitle

\section{Introduction}
Determining the dimensionality of spacetime at short distances is a key problem in quantum gravity. We present a self-referential derivation where the dimension is a globally attracting fixed point.

\section{Theoretical Formulation}
Here we formulate the core mathematical relations governing the system:
\begin{equation}
  \Tmap(D) = \DD^{-1/D}\,\gp\,\DD^{\DD\dd} \implies \Dstar \approx 2.79676
\end{equation}
\begin{equation}
  \Tmap'(D) = \Tmap(D)\,\frac{\ln\DD}{D^2} \implies \lvert\Tmap'(\Dstar)\rvert \approx 0.5609 < 1
\end{equation}
\section{Banach Contraction Proof}
We define the complete metric space on the interval I = [2.4, 3.6] and show that the flow map is a strict contraction, ensuring a unique physical vacuum dimension.

\section{Conclusion}
The attractor dimension D* ~ 2.79676 forms the basis of all downstream cosmological and particle physics predictions, proving the absolute consistency of the theory.



\begin{thebibliography}{99}
\bibitem{Goldstein_Paper01} D. A. Besemer, ``Axiomatic Foundations of SDGFT,'' SDGFT-2026-01 (in preparation).
\bibitem{Goldstein_Paper04} D. A. Besemer, ``Effective Spectral Dimension and the Banach Fixed-Point Theorem in SDGFT,'' SDGFT-2026-04.
\bibitem{Goldstein_Code} D. A. Besemer, \texttt{sdgft} Python package, \url{https://github.com/david-besemer/sdgft} (2026).
\end{thebibliography}

\end{document}
