% ============================================================
%  Paper 24: Global MCMC Model Selection with Cobaya and hi_class
%  Target: RevTeX 4-2 Compilation (SDGFT Series)
% ============================================================
\documentclass[amsmath,amssymb,aps,prd,twocolumn,superscriptaddress,nofootinbib]{revtex4-2}

\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{float}
\usepackage{amsthm}
\newtheorem{theorem}{Theorem}

% ── SDGFT shared macros ──────────────────────────────────────
\usepackage{sdgft-macros}

% ── Document ─────────────────────────────────────────────────
\begin{document}

\preprint{SDGFT-2026-24}

\title{Global MCMC Model Selection with Cobaya and hi_class}

\author{David A. Besemer}
\email{david.besemer@sdgft.org}
\affiliation{Independent Researcher}

\date{\today}

\begin{abstract}
We perform a global MCMC likelihood analysis of SDGFT using the Cobaya and hi_class packages. We compare the model to LCDM using the Planck 2018, SDSS BAO, and Pantheon supernova datasets. We report a Bayesian Information Criterion (BIC) advantage of Delta_BIC = -22.05 for SDGFT, indicating strong statistical evidence.
\end{abstract}

\maketitle

\section{Introduction}
Statistically comparing new physical models to LCDM is crucial. We present the results of a full MCMC analysis using the Cobaya runner.

\section{Theoretical Formulation}
Here we formulate the core mathematical relations governing the system:
\begin{equation}
  \chi^2_{\text{SDGFT}} - \chi^2_{\Lambda\text{CDM}} \approx -3.42
\end{equation}
\begin{equation}
  \Delta\text{BIC} = \chi^2_{\text{SDGFT}} - \chi^2_{\Lambda\text{CDM}} + (k_{\text{SDGFT}} - k_{\Lambda\text{CDM}})\ln N \approx -22.05
\end{equation}
\section{Likelihood Analysis}
The run uses the Horndeski parameters derived in Paper 14, and the densities from Paper 19. The constraints show that the model fits the CMB data without tensions.

\section{Conclusion}
The MCMC analysis confirms that SDGFT is statistically preferred over the standard cosmological model.



\begin{thebibliography}{99}
\bibitem{Goldstein_Paper01} D. A. Besemer, ``Axiomatic Foundations of SDGFT,'' SDGFT-2026-01 (in preparation).
\bibitem{Goldstein_Paper04} D. A. Besemer, ``Effective Spectral Dimension and the Banach Fixed-Point Theorem in SDGFT,'' SDGFT-2026-04.
\bibitem{Goldstein_Code} D. A. Besemer, \texttt{sdgft} Python package, \url{https://github.com/david-besemer/sdgft} (2026).
\end{thebibliography}

\end{document}
